MT @HanBaldwin: Fightin OOVs in German \#twitter

### 2013-07-27 darmstadt_gscl_2013/article_twitter_normalization.tex
minor update

Here once again the question of classification arose but this time
with regard to the reasons, why different tokens could have been
omitted from corresponding applications' dictionaries. In this
respect, division into following groups seemed to be appropriate for
us:
\begin{enumerate}
  \item \textbf{Objective limitedness of machine-readable dictionary
    (MRD)}. To this group we counted words of basic vocabulary which
    did not get into applications' MRD either because they supposedly
    were rare or because they did not exist at the time when
    dictionaries were created. Another reason for inclusion in this
    type was the belonging of a word to an open lexical or
    part-of-speech class (like, for example, named entities or
    interjections) which are usually deliberately not included in MRDs
    due to impossibility to fully cover these classes;\label{dict}
  \item \textbf{Unintended sloppiness of users' input}. In the scope
    of this group we considered unintended typos including unexpected
    truncation of words at the end of Twitter messages\footnote{As is
      generally known, Twitter imposes a strong restriction on the
      length of posted messages which can be no longer than 140
      characters. Upon exceeding this length, tweets get automatically
      truncated to maximal allowed length.};\label{spell}
  \item \textbf{Stylistic specifics of text genre}. This group
    comprised words which could be considered as illegal from the
    point of view of standard language texts but were perfectly valid
    terms in the domain of web discourse and Twitter
    communication.\label{style}
\end{enumerate}

>>>>

Here once again the question of classification arose but this time
with regard to the reasons, why different tokens could have been
omitted from corresponding applications' dictionaries. In this
respect, division into following groups seemed to be appropriate for
us:
\begin{enumerate}
  \item \textbf{Objective limitedness of machine-readable dictionary
    (MRD)}. To this group we counted words of basic vocabulary which
    did not get into applications' MRD either because they supposedly
    were rare or because they did not exist at the time when
    dictionaries were created. Another reason for inclusion in this
    type was the belonging of a word to an open lexical or
    part-of-speech class (like, for example, named entities or
    interjections) which are usually deliberately not included in MRDs
    due to impossibility to fully cover these classes;\label{dict}
  \item \textbf{Unintended sloppiness of users' input}. In the scope
    of this group we considered unintended typos including unexpected
    truncation of words at the end of Twitter messages\footnote{As is
      generally known, Twitter imposes a strong restriction on the
      length of posted messages which can be no longer than 140
      characters. Upon exceeding this length, tweets get automatically
      truncated to maximal allowed length.};\label{spell}
  \item \textbf{Stylistic specifics of text genre}. This group
    comprised words which could be considered as illegal from the
    point of view of standard language but were perfectly valid terms
    in the domain of web discourse and particularly Twitter
    communication.\label{style}
\end{enumerate}
